---
title: "H3"
subtitle: "The Artometrics of A YouTube Dynasty"
format:
  html:
    number-sections: false
    theme: none
    css: artometrics.css
    toc: true
    toc-depth: 2
    toc-title: "IN THIS REPORT"
    toc-location: left
    smooth-scroll: true
    embed-resources: true
    code-fold: true
    code-tools: true
    include-in-header: art-head.html
    include-before-body: art-body.html
editor:
  markdown:
    wrap: 72
---

```{r setup}
#| echo: false
#| warning: false
#| message: false

library(tidyverse)
library(scales)
library(ggtext)
library(lubridate)

dir.create("charts", showWarnings = FALSE)

# Artometrics palette
art_bg        <- "#FAFAF8"
art_cream     <- "#F2F0EB"
art_dark      <- "#1C1C1E"
art_mid       <- "#6B6B6B"
art_highlight <- "#C0392B"
art_secondary <- "#2C3E6B"
art_muted     <- "#D5D5D5"

# Extended palette for multi-series charts
art_purple    <- "#6C3483"
art_teal      <- "#117864"

theme_artometrics <- function() {
  theme_minimal(base_family = "Helvetica") +
    theme(
      plot.background   = element_rect(fill = art_cream, color = NA),
      panel.background  = element_rect(fill = art_cream, color = NA),
      panel.grid.major  = element_line(color = art_muted, linewidth = 0.4),
      panel.grid.minor  = element_blank(),
      plot.title        = element_markdown(size = 14, face = "bold",
                                           color = art_dark),
      plot.subtitle     = element_text(size = 11, color = art_mid),
      plot.caption      = element_text(size = 8, color = art_mid, hjust = 0),
      axis.text         = element_text(size = 9, color = art_mid),
      axis.title        = element_text(size = 10, color = art_dark),
      legend.background = element_rect(fill = art_cream, color = NA),
      legend.text       = element_text(color = art_dark),
      strip.text        = element_text(face = "bold", color = art_dark)
    )
}
```

```{r load-data}
#| echo: false
#| warning: false
#| message: false

h3 <- read_csv(
  "https://raw.githubusercontent.com/Artometrics/h3/main/h3_master.csv"
) |>
  filter(duration_minutes > 1, view_count > 0)

episodes <- read_csv(
  "https://raw.githubusercontent.com/Artometrics/h3/main/h3_podchaser_episodes.csv"
)

reddit <- read_csv("data/h3_reddit_posts.csv")
snark  <- read_csv("data/h3_snark_posts.csv")
```

---

## DATASET CONTEXT

### FOUR CHANNELS, ONE BRAND

The H3 ecosystem is not a single channel — it is a network. h3h3Productions
launched in 2011 as a reaction-and-commentary channel built around the
Fair Use legal fight that briefly made Ethan Klein a cause célèbre in
YouTube creator circles. The H3 Podcast launched in 2017 as a separate
channel and quickly became the brand's primary vehicle. Hila Klein's
channel documents the Teddy Fresh clothing brand. The Ethan Klein channel
captures solo content and live streams. This report analyzes all four:
**1,638 videos** after filtering Shorts and zero-view uploads from the
original 1,876-video pull via the YouTube Data API v3.

### THE ERA STRUCTURE

H3's trajectory cannot be understood without the era framework.
The podcast's baseline (2017–2020) established the format: long-form
conversation between Ethan and Hila, irregular cadence, modest but
loyal viewership. The **Frenemies Era** (September 2020 – June 2021)
is the single most-watched stretch in H3 Podcast history — nine months
in which Ethan co-hosted with Trisha Paytas, generating a level of
weekly engagement the show has never approached since. The **Leftovers
Era** (September 2021 – October 2023) brought a political co-host in
Hasan Piker, a different kind of audience, and a deeper ideological
identity for the brand. When Leftovers ended over disagreements about
the Israel-Palestine conflict, H3 entered its current post-format phase:
fewer episodes, longer runtimes, a shrinking but committed core audience.

### THE DATA SOURCES

The core dataset was built from scratch using the YouTube Data API v3,
stored at `github.com/Artometrics/h3`. Podcast episode metadata comes
from the Podchaser API (680 episodes, April 2026 pull). Reddit post data
was pulled from the Arctic Shift Reddit archive, covering
**r/h3h3productions** (749,974 posts, 2014–2026) and
**r/h3snark** (25,766 posts, April 2023–2026) — the fan sub and the
critic sub, both active during the most contentious period in the brand's
history.

### WHY THIS REPORT EXISTS

H3 is one of the most data-rich creator brands on the internet. The
combination of YouTube longevity (13 years), a documented era structure,
an unusually organized fan and critic community, and a clothing brand
with its own Wikipedia page creates a dataset that rewards analysis.
This report does not take a position on the controversies. It reads the
numbers and describes what they show.

---

## FAST FACTS

```{=html}
<style>
  .facts-grid {
    display: grid;
    grid-template-columns: repeat(3, 1fr);
    gap: 16px;
    margin: 24px 0 32px 0;
  }
  .fact-box {
    background: #F2F0EB;
    border-left: 4px solid #C0392B;
    padding: 18px 20px;
    border-radius: 2px;
  }
  .fact-number {
    display: block;
    font-size: 1.75rem;
    font-weight: 700;
    color: #C0392B;
    line-height: 1.1;
    margin-bottom: 6px;
    font-family: Helvetica, sans-serif;
  }
  .fact-label {
    display: block;
    font-size: 0.82rem;
    color: #6B6B6B;
    line-height: 1.45;
    font-family: Helvetica, sans-serif;
  }
  @media (max-width: 700px) {
    .facts-grid { grid-template-columns: 1fr 1fr; }
  }
</style>

<div class="facts-grid">
  <div class="fact-box">
    <span class="fact-number">3.24B</span>
    <span class="fact-label">Total views across all four H3 channels, 2013–2026 — enough to give every person on Earth nearly half a view</span>
  </div>
  <div class="fact-box">
    <span class="fact-number">1,638</span>
    <span class="fact-label">Videos analyzed after filtering Shorts and zero-view uploads from the original 1,876-video pull</span>
  </div>
  <div class="fact-box">
    <span class="fact-number">4.5×</span>
    <span class="fact-label">How much harder h3h3Productions hits per video vs. the H3 Podcast — 4.78M median vs. 1.05M</span>
  </div>
  <div class="fact-box">
    <span class="fact-number">9 months</span>
    <span class="fact-label">The entire Frenemies Era — the most-watched stretch in H3 Podcast history, Sep 2020 to Jun 2021</span>
  </div>
  <div class="fact-box">
    <span class="fact-number">680</span>
    <span class="fact-label">H3 Podcast episodes analyzed via Podchaser API — median runtime grew from 42 minutes in 2017 to 220+ by 2024</span>
  </div>
  <div class="fact-box">
    <span class="fact-number">353</span>
    <span class="fact-label">r/h3snark indexed activity at its April 2025 peak — 3.5× its own average, triggered by the iDubbbz Content Cop</span>
  </div>
</div>
```

---

## SQL EXHIBIT

The query below mirrors the R cleaning logic used in this report. It is
display-only — this dataset lives in R and GitHub, not a relational
database — but it documents the filtering decisions in a language built
for them.

<details>
<summary><span class="art-lang-tag art-lang-sql">SQL</span> &nbsp;View filtering logic</summary>

```sql
-- H3 Master Dataset: Filter and Prepare
-- Source: YouTube Data API v3 via Artometrics Original Pull
-- Mirrors: load-data and clean-data chunks in h3.qmd

SELECT
    channel,
    title,
    date,
    view_count,
    duration_minutes,
    DATE_TRUNC('month', date)   AS month_floor,
    DATE_TRUNC('year',  date)   AS year_floor,

    CASE
        WHEN date < '2020-09-15'                              THEN 'Podcast Launch'
        WHEN date BETWEEN '2020-09-15' AND '2021-06-08'      THEN 'Frenemies Era'
        WHEN date BETWEEN '2021-09-26' AND '2023-10-07'      THEN 'Leftovers Era'
        ELSE                                                       'Post-Leftovers'
    END AS era

FROM h3_master

-- Exclude Shorts (< 2 min) and zero-view uploads
WHERE duration_minutes > 1
  AND view_count       > 0

ORDER BY date ASC;


-- Reddit indexing query (mirrors Chart 3 construction)
-- Indexes each subreddit's monthly post count to its own average

WITH monthly_counts AS (
    SELECT
        source,
        DATE_TRUNC('month', date) AS month,
        COUNT(*)                  AS n_posts
    FROM (
        SELECT 'r/h3h3productions' AS source, date FROM h3_reddit_posts
        UNION ALL
        SELECT 'r/h3snark'         AS source, date FROM h3_snark_posts
    ) combined
    GROUP BY source, DATE_TRUNC('month', date)
),

subreddit_averages AS (
    SELECT
        source,
        AVG(n_posts) AS avg_posts
    FROM monthly_counts
    GROUP BY source
)

SELECT
    mc.source,
    mc.month,
    mc.n_posts,
    ROUND((mc.n_posts / sa.avg_posts) * 100, 1) AS index
FROM monthly_counts mc
JOIN subreddit_averages sa
  ON mc.source = sa.source
WHERE mc.month >= '2023-04-01'
ORDER BY mc.source, mc.month;
```

</details>

---

## PYTHON EDA

The script below documents the initial data pull and exploratory checks
run before any R charts were built. It covers the YouTube API pull
structure and basic diagnostic summaries across all four channels.

<details>
<summary><span class="art-lang-tag art-lang-python">Python</span> &nbsp;View EDA notebook</summary>

```python
# H3 Artometrics — Python EDA
# Purpose: YouTube API pull structure + dataset diagnostics
# Run before R chart build to validate data shape and coverage

import pandas as pd
import numpy as np
from googleapiclient.discovery import build

# ── 1. YouTube API Pull Structure ────────────────────────────────────────────

# Channel IDs — H3 network
CHANNEL_IDS = {
    "h3h3Productions": "UCDWIvJwLJsE4LG1Atne2blQ",
    "H3 Podcast":      "UCLtREklEc2upvIiudBMBmJg",
    "Hila Klein":      "UCgPTHMbDMCkDcGsZsKnJFGQ",
    "Ethan Klein":     "UCiDNNUJRqSHEtjGJO1m5mQA"
}

# API call pattern (executed separately, key stored in Google Cloud)
# youtube = build("youtube", "v3", developerKey=API_KEY)
# Results stored to data/h3_master.csv — 1,876 raw videos

# ── 2. Load Master Dataset ───────────────────────────────────────────────────

df = pd.read_csv("data/h3_master.csv", parse_dates=["date"])
df_clean = df[(df["duration_minutes"] > 1) & (df["view_count"] > 0)].copy()

print(f"Raw videos:    {len(df):,}")
print(f"After filter:  {len(df_clean):,}")
print(f"Dropped:       {len(df) - len(df_clean):,}")
# Raw: 1,876 | After filter: 1,638 | Dropped: 238

# ── 3. Channel Coverage ──────────────────────────────────────────────────────

channel_summary = (
    df_clean
    .groupby("channel")
    .agg(
        videos      = ("view_count", "count"),
        total_views = ("view_count", "sum"),
        median_views= ("view_count", "median"),
        first_video = ("date", "min"),
        last_video  = ("date", "max")
    )
    .sort_values("total_views", ascending=False)
)
print(channel_summary.to_string())

# ── 4. Era Flag ──────────────────────────────────────────────────────────────

def assign_era(date):
    if date < pd.Timestamp("2020-09-15"):
        return "Podcast Launch"
    elif date < pd.Timestamp("2021-06-08"):
        return "Frenemies Era"
    elif date < pd.Timestamp("2023-10-07"):
        return "Leftovers Era"
    else:
        return "Post-Leftovers"

df_clean["era"] = df_clean["date"].apply(assign_era)

era_views = (
    df_clean[df_clean["channel"] == "H3 Podcast"]
    .groupby("era")["view_count"]
    .agg(["sum", "median", "count"])
    .rename(columns={"sum": "total", "median": "median", "count": "videos"})
)
print(era_views)

# ── 5. Podchaser Episode Diagnostics ────────────────────────────────────────

eps = pd.read_csv("data/h3_podchaser_episodes.csv", parse_dates=["airDate"])

print(f"\nEpisodes total: {len(eps):,}")
print(f"Date range:     {eps['airDate'].min().date()} → {eps['airDate'].max().date()}")
print(f"Median runtime: {eps['length_min'].median():.0f} min")
print(f"Max runtime:    {eps['length_min'].max():.0f} min")
print(f"Missing duration: {eps['length_min'].isna().sum()} episodes")

# ── 6. Reddit Coverage Check ─────────────────────────────────────────────────

fans  = pd.read_csv("data/h3_reddit_posts.csv",  parse_dates=["date", "month"])
snark = pd.read_csv("data/h3_snark_posts.csv",   parse_dates=["date", "month"])

print(f"\nr/h3h3productions: {len(fans):,} posts | {fans['date'].min().date()} → {fans['date'].max().date()}")
print(f"r/h3snark:         {len(snark):,} posts | {snark['date'].min().date()} → {snark['date'].max().date()}")

# Overlap window for Chart 3 indexing
overlap_start = pd.Timestamp("2023-04-01")
fans_overlap  = fans[fans["date"] >= overlap_start]
snark_overlap = snark[snark["date"] >= overlap_start]
print(f"\nOverlap window (Apr 2023+): fans={len(fans_overlap):,} | snark={len(snark_overlap):,}")
```

</details>

---

## CHART 1 — THE ERA TIMELINE

### Monthly H3 Podcast Views, 2017–2026

```{r chart1-era-timeline}
#| echo: false
#| warning: false
#| message: false
#| fig-width: 10
#| fig-height: 6.5

era_lines <- data.frame(
  date = as.Date(c(
    "2020-09-15",
    "2021-06-08",
    "2021-09-26",
    "2023-10-07"
  )),
  label = c(
    "Frenemies\nPremiere",
    "Frenemies\nFinale",
    "Leftovers\nPremiere",
    "Leftovers\nFinale"
  ),
  color = c(
    art_highlight,
    art_highlight,
    art_secondary,
    art_secondary
  ),
  vjust = c(1.3, 4.5, 1.3, 1.3)
)

p1 <- h3 |>
  filter(channel == "H3 Podcast") |>
  mutate(month_floor = floor_date(date, "month")) |>
  group_by(month_floor) |>
  summarise(monthly_views = sum(view_count, na.rm = TRUE)) |>
  ggplot(aes(x = month_floor, y = monthly_views)) +
  geom_area(fill = art_secondary, alpha = 0.15) +
  geom_line(color = art_secondary, linewidth = 0.8) +
  geom_vline(
    data = era_lines,
    aes(xintercept = date, color = color),
    linetype = "dashed",
    linewidth = 0.6
  ) +
  geom_text(
    data = era_lines,
    aes(x = date, y = Inf, label = label, color = color, vjust = vjust),
    hjust = -0.08,
    size = 2.7, fontface = "bold"
  ) +
  annotate(
    "point",
    x = as.Date("2017-08-01"),
    y = 25000000,
    color = art_highlight,
    size = 3
  ) +
  annotate(
    "text",
    x = as.Date("2017-08-01"),
    y = 25000000,
    label = "Podcast Launch\nHoneymoon",
    hjust = -0.1,
    vjust = 0.5,
    size = 2.7,
    color = art_highlight,
    fontface = "bold"
  ) +
  scale_color_identity() +
  scale_y_continuous(labels = label_number(scale = 1e-6, suffix = "M")) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  labs(
    title    = "THE <span style='color:#C0392B'>**FRENEMIES ERA**</span> IS A MOUNTAIN ON THE GRAPH",
    subtitle = "Monthly Total Views, H3 Podcast Channel, 2017–2026",
    x        = NULL,
    y        = "Monthly Views",
    caption  = "Data: YouTube Data API v3 | Artometrics Original Dataset\n— ARTOMETRICS"
  ) +
  theme_artometrics()

p1

ggsave("chart1_era_timeline.png", plot = p1,
       path = "charts", width = 12, height = 7, dpi = 300, bg = "white")
```

### THE FRENEMIES MOUNTAIN

The shape of this chart tells you almost everything you need to know
about the H3 Podcast's commercial arc. From 2017 to mid-2020, the show
built a reliable if unspectacular baseline — a few million views per
month, loyal audience, consistent output. Then Trisha Paytas joined as
co-host in September 2020 and the graph becomes a different document.
Monthly views tripled within weeks. The peak months of the Frenemies
Era outperformed the entire preceding three years of the podcast, and
the show did it in nine months.

### THE CLIFF IS PERMANENT

When Frenemies ended in June 2021 — abruptly, on-camera, mid-episode —
views dropped back toward baseline within a single month. Leftovers
launched that September and added a new audience (Hasan Piker's
political fanbase), generating a secondary bump visible in the 2022
data. But it never approached Frenemies numbers. After Leftovers ended
in October 2023, the chart enters its current phase: a slow, grinding
decline with no structural catalyst in sight. The mountain is the story.
Everything else is the aftermath.

### WHAT THE BASELINE TELLS YOU

Even at its post-2023 lows, the H3 Podcast pulls millions of monthly
views. The brand did not collapse — it contracted to its core. The
audience that remains watches longer episodes with more commitment than
the casual Frenemies-era viewer. The cliff looks dramatic on the chart
because Frenemies was genuinely anomalous. The current numbers are not
a failure; they are what a major podcast looks like without a viral
co-host dynamic driving weekly drama.

---

## CHART 2 — THE DURATION DRIFT

### Median Episode Length by Month, H3 Podcast, 2017–2026

```{r chart2-duration-drift}
#| echo: false
#| warning: false
#| message: false
#| fig-width: 10
#| fig-height: 6.5

era_levels_dur <- c(
  "Podcast Launch (2017–Sep 2020)",
  "Frenemies Era (Sep 2020–Jun 2021)",
  "Leftovers Era (Jun 2021–Oct 2023)",
  "Post-Leftovers (Oct 2023–2026)"
)

era_colors_dur <- c(
  "Podcast Launch (2017–Sep 2020)"    = art_secondary,
  "Frenemies Era (Sep 2020–Jun 2021)" = art_highlight,
  "Leftovers Era (Jun 2021–Oct 2023)" = art_purple,
  "Post-Leftovers (Oct 2023–2026)"    = art_teal
)

p2_data <- episodes |>
  mutate(
    airDate = as.Date(airDate),
    month   = floor_date(airDate, "month"),
    era     = case_when(
      airDate < as.Date("2020-09-15")                                    ~
        "Podcast Launch (2017–Sep 2020)",
      airDate >= as.Date("2020-09-15") & airDate < as.Date("2021-06-08") ~
        "Frenemies Era (Sep 2020–Jun 2021)",
      airDate >= as.Date("2021-06-08") & airDate < as.Date("2023-10-07") ~
        "Leftovers Era (Jun 2021–Oct 2023)",
      TRUE ~
        "Post-Leftovers (Oct 2023–2026)"
    ),
    era = factor(era, levels = era_levels_dur)
  ) |>
  group_by(month, era) |>
  summarise(median_min = median(length_min, na.rm = TRUE), .groups = "drop")

p2 <- ggplot(p2_data, aes(x = month, y = median_min)) +
  geom_point(aes(color = era), size = 2, alpha = 0.5) +
  geom_smooth(
    method    = "loess",
    span      = 0.25,
    se        = FALSE,
    color     = art_dark,
    linewidth = 1.2
  ) +
  geom_hline(
    yintercept = 180,
    linetype   = "dashed",
    color      = art_mid,
    linewidth  = 0.5
  ) +
  annotate(
    "text",
    x     = as.Date("2017-06-01"),
    y     = 184,
    label = "3-hour mark",
    color = art_mid,
    size  = 3.2,
    hjust = 0
  ) +
  scale_color_manual(
    values = era_colors_dur,
    guide  = guide_legend(nrow = 2, override.aes = list(size = 3, alpha = 1))
  ) +
  scale_x_date(
    date_breaks = "1 year",
    date_labels = "%Y",
    expand      = c(0.01, 0)
  ) +
  scale_y_continuous(
    breaks = seq(0, 300, by = 60),
    labels = function(x) paste0(x, " min"),
    expand = c(0.02, 0)
  ) +
  labs(
    title    = "H3 EPISODES GOT LONGER EVERY YEAR — <span style='color:#C0392B'>**AND NEVER CAME BACK**</span>",
    subtitle = "Median episode duration by month · Smoothed trend line · 680 episodes",
    x        = NULL,
    y        = "Median Duration (minutes)",
    color    = NULL,
    caption  = "Data: Podchaser API, pulled April 2026 | Artometrics Original Dataset\n— ARTOMETRICS"
  ) +
  theme_artometrics() +
  theme(
    legend.position    = "bottom",
    legend.key.size    = unit(0.8, "lines"),
    legend.spacing.x   = unit(0.4, "cm"),
    panel.grid.major.x = element_blank()
  )

p2

ggsave("chart2_duration_drift.png", plot = p2,
       path = "charts", width = 12, height = 7, dpi = 300, bg = "white")
```

### 42 MINUTES TO 4 HOURS: THE CREEP NOBODY NOTICED

When H3 launched the podcast in 2017, the median episode ran **42
minutes**. That's a commute. By 2024, the median had crossed **220
minutes** — longer than most feature films. The chart shows this wasn't
a sudden format change; it was a slow, continuous drift upward that
compounded year over year until a new normal was established. No single
episode caused it. No announcement reset it. The show just kept going
longer, and the audience kept watching.

### THE FLOOR SHIFT OF 2022

The clearest structural break in the duration data isn't a spike — it's
a floor shift. Before 2022, monthly medians regularly dipped below 120
minutes. After 2022, they never did. The show locked into 3-hour-plus
territory and stayed there. Leftovers (2021) normalized the extended
format; by the time it ended (2023), the audience had been conditioned
to expect marathon sessions as the default. That conditioning didn't
reverse when Leftovers ended.

### FEWER EPISODES, LONGER RUNTIME — THE 2024 PARADOX

In 2024, H3 published far fewer episodes than in prior years — but
duration hit its all-time high, with months regularly clearing
**220–240 minutes**. The show was publishing less but asking more from
the audience that stayed. Each episode became a larger commitment, not
a smaller one. The fans who remained weren't casual — they were in for
4 hours at a time. Whether that is sustainable is a different question.
The data just shows it happened.

---

## CHART 3 — THE FAN VS. CRITIC DIVIDE

### Reddit Post Volume Indexed by Subreddit, Apr 2023–Mar 2026

```{r chart3-reddit-activity}
#| echo: false
#| warning: false
#| message: false
#| fig-width: 10
#| fig-height: 6.5

# Build combined indexed dataset
# Overlap window: April 2023 onward (when both subs exist)
window_start <- as.Date("2023-04-01")

fan_monthly <- reddit |>
  filter(month >= window_start) |>
  count(month) |>
  mutate(source = "r/h3h3productions (Fans)")

snark_monthly <- snark |>
  filter(month >= window_start) |>
  count(month) |>
  mutate(source = "r/h3snark (Critics)")

combined <- bind_rows(fan_monthly, snark_monthly) |>
  group_by(source) |>
  mutate(index = (n / mean(n, na.rm = TRUE)) * 100) |>
  ungroup()

# Key annotated points
key_points <- combined |>
  filter(
    (source == "r/h3snark (Critics)" & month == as.Date("2025-04-01")) |
    (source == "r/h3h3productions (Fans)" & month == as.Date("2025-04-01"))
  ) |>
  mutate(
    label = case_when(
      source == "r/h3snark (Critics)"      ~ paste0(round(index), " (peak)"),
      source == "r/h3h3productions (Fans)" ~ paste0(round(index))
    ),
    vjust = case_when(
      source == "r/h3snark (Critics)"      ~ -0.8,
      source == "r/h3h3productions (Fans)" ~ 1.6
    )
  )

vlines <- data.frame(
  date  = as.Date(c("2023-10-07", "2025-01-31", "2025-04-16")),
  label = c(
    "Leftovers ends\n+ Gaza fallout",
    "Content Nuke\n– Hasan",
    "Content Cop\n– H3"
  ),
  y = c(340, 290, 240)
)

p3 <- ggplot(combined, aes(x = month, y = index, color = source)) +
  geom_line(linewidth = 0.9) +
  geom_hline(
    yintercept = 100,
    linetype   = "dashed",
    color      = art_mid,
    linewidth  = 0.4
  ) +
  geom_vline(
    data = vlines,
    aes(xintercept = date),
    color = art_mid, linetype = "dotted", linewidth = 0.6,
    inherit.aes = FALSE
  ) +
  geom_text(
    data = vlines,
    aes(x = date, y = y, label = label),
    color = art_mid, size = 2.5, fontface = "bold",
    hjust = -0.07, lineheight = 0.9,
    inherit.aes = FALSE
  ) +
  geom_point(
    data = key_points,
    aes(x = month, y = index),
    size = 2.5,
    inherit.aes = TRUE
  ) +
  geom_text(
    data = key_points,
    aes(x = month, y = index, label = label, vjust = vjust),
    size = 2.6, fontface = "bold",
    show.legend = FALSE
  ) +
  scale_color_manual(values = c(
    "r/h3h3productions (Fans)" = art_secondary,
    "r/h3snark (Critics)"      = art_highlight
  )) +
  scale_x_date(date_breaks = "3 months", date_labels = "%b %Y") +
  scale_y_continuous(
    expand = c(0.1, 0)
  ) +
  labs(
    title    = "FANS AND CRITICS RESPOND TO <span style='color:#C0392B'>**COMPLETELY DIFFERENT TRIGGERS**</span>",
    subtitle = "Monthly Post Volume Indexed to Each Subreddit's Own Average (100 = Baseline) · Apr 2023–Mar 2026",
    x        = NULL,
    y        = "Indexed Activity (100 = Avg)",
    color    = NULL,
    caption  = "Source: Arctic Shift Reddit Archive · Artometrics Original Dataset\n— ARTOMETRICS"
  ) +
  theme_artometrics() +
  theme(
    legend.position    = "bottom",
    legend.key.size    = unit(0.8, "lines"),
    panel.grid.major.x = element_blank(),
    axis.text.x        = element_text(angle = 30, hjust = 1)
  )

p3

ggsave("chart3_reddit_activity.png", plot = p3,
       path = "charts", width = 12, height = 7, dpi = 300, bg = "white")
```

### THE CRITIC COMMUNITY PEAKED WHILE FANS WERE CHECKED OUT

The indexed chart removes the raw scale difference between subreddits
and asks a cleaner question: when did each community spike relative to
its own normal? The answer is almost never at the same time. When the
iDubbbz Content Cop dropped on April 16, 2025 — the first Content Cop
in years, explicitly targeting the H3 brand — r/h3snark hit its
all-time peak at more than **3.5× its own average**. The fan sub
barely registered the same event. The two communities were watching
completely different shows.

### KLEIN KILLED HIS OWN CRITIC COMMUNITY

The cliff in the snark data after May 2025 isn't a controversy dying
down — it's a subreddit going dark. After Klein issued copyright claims
against r/h3snark moderators and threatened legal action, the sub
announced an indefinite hiatus. The index collapsed to near zero within
weeks. The fan sub, meanwhile, continued its slow decline — below its
own average but still functional. The snark community didn't fade. It
was shut down. That distinction matters: one line represents organic
audience erosion, the other represents a legal intervention.

### FANS ARE IN LONG-TERM DECLINE TOO

The blue line tells its own quieter story. The fan sub never spikes
the way snark does — no single event moves it dramatically above
baseline. But the trend is unmistakably downward. The community isn't
in crisis; it's in slow erosion. Fewer new things to discuss, fewer
viral moments to dissect, fewer reasons to post. The legal drama —
the Content Cop, the streamer lawsuits — barely registered. Whatever
drives fan engagement on r/h3h3productions, it isn't courtroom news.

---

## LIMITATIONS

### DATA COVERAGE GAPS

The YouTube data captures view counts as of the April 2026 pull — not
at time of publication. Older videos have had years to accumulate views
through algorithmic recommendations and search, which means early
h3h3Productions videos are systematically over-represented in lifetime
view totals relative to their original performance. The era-based
analysis on the H3 Podcast channel is less affected because the
comparison is within-channel across time.

### REDDIT ARCHIVE COMPLETENESS

The Arctic Shift Reddit archive is comprehensive but not guaranteed
complete. Deleted posts, removed comments, and accounts banned before
archival are absent from the dataset. The r/h3snark data begins in
April 2023 — the sub's founding — so pre-2023 critical community
activity is unrepresented. Any conclusions about the fan-vs-critic
dynamic are bounded by that window.

### PODCHASER EPISODE METADATA

Episode duration data from Podchaser is self-reported by the show and
may include inconsistencies for older episodes, live streams published
as podcast episodes, and bonus or clip content. Episodes with missing
duration values were excluded from Chart 2 analysis.

### INDEXING METHODOLOGY

Chart 3 indexes each subreddit to its own average across the Apr
2023–Mar 2026 window. This removes absolute scale differences between
subreddits but also means a subreddit with very low activity in early
months will show inflated index values in later high-activity periods.
The r/h3snark baseline is built on its full available history, which
starts at launch — a period of lower activity — and may slightly
inflate peak readings relative to a steadier baseline.

---

## CONCLUSION

The H3 data tells a story about what happens when a creator brand
builds its peak moment around someone else. The Frenemies Era was
genuinely anomalous — nine months of co-host-driven drama that
tripled the podcast's monthly viewership and created a ceiling the
show has never approached since. The chart is unambiguous about this.
The current audience is not a collapse; it is a correction back to
what the brand can sustain on its own terms.

The duration data adds a different dimension. The show that emerged
from the Frenemies aftermath is structurally different from the one
that preceded it — longer, less frequent, more demanding. Whether
that format is a creative choice or a symptom of a contracting
audience is a question the data cannot answer. Both explanations fit
the numbers.

The Reddit chart is the most structurally interesting of the three.
It documents not just audience behavior but audience management: a
creator using legal tools to suppress a critic community. The snark
subreddit's cliff is not organic. It is the result of a deliberate
intervention. The fan sub's slower decline runs in parallel and
suggests the underlying engagement problem would exist regardless.
Two different communities, two different trajectories, one brand
caught between them.

*— KSM*

---

## REFERENCES

- YouTube Data API v3. Google.
  https://developers.google.com/youtube/v3

- Artometrics Original Dataset (April 2026). *H3 Podcast YouTube
  Network, 2013–2026*. Compiled via YouTube Data API v3.
  https://github.com/Artometrics/h3

- Podchaser. (2026). *H3 Podcast episode data, 2017–2026*.
  Retrieved via Podchaser API v1.
  https://api.podchaser.com

- Arctic Shift Reddit Archive. (2026). *r/h3h3productions and
  r/h3snark post data*. Retrieved April 2026.
  https://arctic-shift.photon-reddit.com

- Wikimedia Foundation. (2026). *Wikipedia pageview statistics*.
  Retrieved via Wikimedia REST API.
  https://wikimedia.org/api/rest_v1/

- Google Trends. (2026). *Search interest data: h3h3, ethan klein,
  frenemies, teddy fresh*. Retrieved via gtrendsR v1.5.2.
  https://trends.google.com

---

## EDITOR'S NOTE

This report was researched, written, designed, and produced in active
collaboration with Claude AI (Anthropic). The data pipeline, statistical
analysis, chart design, written analysis, narrative structure, and
visual styling were all developed through a directed partnership between
human editorial judgment and AI execution.

Artometrics was built on the premise that rigorous analysis and honest
process are not in conflict. The research questions, editorial instincts,
interpretive framing, and brand vision are ours. The execution — every
line of R code, every paragraph of analysis, every design decision —
was a collaboration. We document this not as a disclaimer but as a
description of how we actually work, and as a position: we believe this
is what serious data journalism looks like when the tools available are
used honestly and at full capacity.

*— Artometrics Editorial*

---

## THANK YOU

This report uses data from the YouTube Data API v3, the Podchaser API,
and the Arctic Shift Reddit Archive. The TidyTuesday community and the
broader open data ecosystem make work like this possible.

If you have feedback, corrections, or data to add, reach out at
**artometrics.com**.
