---
title: "THE ARTOMETRICS OF H3"
format:
  html:
    number-sections: false
    theme: none
    css: artometrics.css
    toc: true
    toc-depth: 2
    toc-title: "IN THIS REPORT"
    toc-location: left
    smooth-scroll: true
    embed-resources: true
  pdf:
    number-sections: false
editor:
  markdown:
    wrap: 72
---

```{r setup}
#| echo: false
#| warning: false
#| message: false

library(tidyverse)
library(scales)
library(ggtext)
library(lubridate)
library(httr)
library(jsonlite)
library(gtrendsR)

# Artometrics palette
art_bg        <- "#FAFAF8"
art_cream     <- "#F2F0EB"
art_dark      <- "#1C1C1E"
art_mid       <- "#6B6B6B"
art_highlight <- "#C0392B"
art_secondary <- "#2C3E6B"
art_muted     <- "#D5D5D5"

# Extended palette for multi-series charts
art_purple    <- "#6C3483"
art_teal      <- "#117864"

theme_artometrics <- function() {
  theme_minimal(base_family = "Helvetica") +
    theme(
      plot.background  = element_rect(fill = art_cream, color = NA),
      panel.background = element_rect(fill = art_cream, color = NA),
      panel.grid.major = element_line(color = art_muted, linewidth = 0.4),
      panel.grid.minor = element_blank(),
      plot.title       = element_markdown(size = 14, face = "bold",
                                          color = art_dark),
      plot.subtitle    = element_text(size = 11, color = art_mid),
      plot.caption     = element_text(size = 8, color = art_mid, hjust = 0),
      axis.text        = element_text(size = 9, color = art_mid),
      axis.title       = element_text(size = 10, color = art_dark),
      legend.background = element_rect(fill = art_cream, color = NA),
      legend.text      = element_text(color = art_dark),
      strip.text       = element_text(face = "bold", color = art_dark)
    )
}
```

```{r load-data}
#| echo: false
#| warning: false
#| message: false

h3 <- read_csv(
  "https://raw.githubusercontent.com/Artometrics/h3/main/h3_master.csv"
) |>
  filter(duration_minutes > 1, view_count > 0)

wiki <- read_csv(
  "https://raw.githubusercontent.com/Artometrics/h3/main/h3_wikipedia.csv"
)

trends <- read_csv(
  "https://raw.githubusercontent.com/Artometrics/h3/main/h3_trends.csv"
) |>
  filter(date >= as.Date("2012-01-01"))

episodes <- read_csv(
  "https://raw.githubusercontent.com/Artometrics/h3/main/h3_podchaser_episodes.csv"
)
```

## FAST FACTS

```{=html}
<style>
  .facts-grid {
    display: grid;
    grid-template-columns: repeat(3, 1fr);
    gap: 16px;
    margin: 24px 0 32px 0;
  }
  .fact-box {
    background: #F2F0EB;
    border-left: 4px solid #C0392B;
    padding: 18px 20px;
    border-radius: 2px;
  }
  .fact-number {
    display: block;
    font-size: 1.75rem;
    font-weight: 700;
    color: #C0392B;
    line-height: 1.1;
    margin-bottom: 6px;
    font-family: Helvetica, sans-serif;
  }
  .fact-label {
    display: block;
    font-size: 0.82rem;
    color: #6B6B6B;
    line-height: 1.45;
    font-family: Helvetica, sans-serif;
  }
  @media (max-width: 700px) {
    .facts-grid { grid-template-columns: 1fr 1fr; }
  }
</style>

<div class="facts-grid">
  <div class="fact-box">
    <span class="fact-number">3.24B</span>
    <span class="fact-label">Total views across all four H3 channels, 2013–2026 — enough to give every person on Earth a nearly half-view</span>
  </div>
  <div class="fact-box">
    <span class="fact-number">1,638</span>
    <span class="fact-label">Videos analyzed after filtering Shorts and zero-view uploads from the original 1,876-video pull</span>
  </div>
  <div class="fact-box">
    <span class="fact-number">4.5×</span>
    <span class="fact-label">How much harder h3h3Productions hits per video vs. the H3 Podcast — 4.78M median vs. 1.05M</span>
  </div>
  <div class="fact-box">
    <span class="fact-number">9 months</span>
    <span class="fact-label">The entire Frenemies Era — the most-watched stretch in H3 Podcast history, Sep 2020 to Jun 2021</span>
  </div>
  <div class="fact-box">
    <span class="fact-number">14,487</span>
    <span class="fact-label">Wikipedia pageviews for the H3 Podcast article in May 2025 — its all-time single-month peak</span>
  </div>
  <div class="fact-box">
    <span class="fact-number">88 / 100</span>
    <span class="fact-label">"Ethan Klein" Google search interest at the Frenemies Finale in June 2021 — the highest the personal brand ever indexed</span>
  </div>
</div>
```

---

## CHART 1 — THE ERA TIMELINE

### Monthly H3 Podcast Views, 2017–2026

```{r chart1-era-timeline}
#| echo: false
#| warning: false
#| message: false
#| fig-width: 10
#| fig-height: 6.5

era_lines <- data.frame(
  date = as.Date(c(
    "2020-09-15",
    "2021-06-08",
    "2021-09-26",
    "2023-10-07"
  )),
  label = c(
    "Frenemies\nPremiere",
    "Frenemies\nFinale",
    "Leftovers\nPremiere",
    "Leftovers\nFinale"
  ),
  color = c(
    art_highlight,
    art_highlight,
    art_secondary,
    art_secondary
  ),
  vjust = c(1.3, 4.5, 1.3, 1.3)
)

p1 <- h3 |>
  filter(channel == "H3 Podcast") |>
  mutate(month_floor = floor_date(date, "month")) |>
  group_by(month_floor) |>
  summarise(monthly_views = sum(view_count, na.rm = TRUE)) |>
  ggplot(aes(x = month_floor, y = monthly_views)) +
  geom_area(fill = art_secondary, alpha = 0.15) +
  geom_line(color = art_secondary, linewidth = 0.8) +
  geom_vline(
    data = era_lines,
    aes(xintercept = date, color = color),
    linetype = "dashed",
    linewidth = 0.6
  ) +
  geom_text(
    data = era_lines,
    aes(x = date, y = Inf, label = label, color = color, vjust = vjust),
    hjust = -0.08,
    size = 2.7, fontface = "bold"
  ) +
  annotate(
    "point",
    x = as.Date("2017-08-01"),
    y = 25000000,
    color = art_highlight,
    size = 3
  ) +
  annotate(
    "text",
    x = as.Date("2017-08-01"),
    y = 25000000,
    label = "Podcast Launch\nHoneymoon",
    hjust = -0.1,
    vjust = 0.5,
    size = 2.7,
    color = art_highlight,
    fontface = "bold"
  ) +
  scale_color_identity() +
  scale_y_continuous(labels = label_number(scale = 1e-6, suffix = "M")) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  labs(
    title    = "THE <span style='color:#C0392B'>**FRENEMIES ERA**</span> IS A MOUNTAIN ON THE GRAPH",
    subtitle = "Monthly Total Views, H3 Podcast Channel, 2017–2026",
    x        = NULL,
    y        = "Monthly Views",
    caption  = "Data: YouTube Data API v3 | Artometrics Original Dataset\n— ARTOMETRICS"
  ) +
  theme_artometrics()

p1

ggsave("chart1_era_timeline.png", plot = p1,
       path = ".", width = 12, height = 7, dpi = 300, bg = "white")
```

### [PLACEHOLDER — analysis coming]

---

## CHART 2 — THE CHANNEL PORTFOLIO

### Per-Video View Distribution, All 4 Channels

```{r chart2-channel-distribution}
#| echo: false
#| warning: false
#| message: false
#| fig-width: 10
#| fig-height: 6.5

channel_order <- h3 |>
  group_by(channel) |>
  summarise(med = median(view_count, na.rm = TRUE)) |>
  arrange(med) |>
  pull(channel)

channel_colors <- c(
  "h3h3Productions" = art_highlight,
  "H3 Podcast"      = art_secondary,
  "Hila Klein"      = art_purple,
  "Ethan Klein"     = art_teal
)

channel_medians <- h3 |>
  group_by(channel) |>
  summarise(
    med      = median(view_count, na.rm = TRUE),
    n_videos = n()
  ) |>
  mutate(channel = factor(channel, levels = channel_order))

p2 <- h3 |>
  mutate(channel = factor(channel, levels = channel_order)) |>
  ggplot(aes(x = channel, y = view_count, fill = channel, color = channel)) +
  geom_violin(alpha = 0.18, color = NA, trim = TRUE) +
  geom_boxplot(
    width = 0.12, fill = art_cream, outlier.shape = NA,
    aes(color = channel), linewidth = 0.6
  ) +
  stat_summary(
    fun = median, geom = "point",
    size = 3.5, color = art_highlight, shape = 21,
    aes(fill = channel)
  ) +
  geom_text(
    data = channel_medians,
    aes(x = channel, y = med,
        label = paste0(round(med / 1e6, 2), "M\nmedian")),
    nudge_x = 0.28, size = 2.8, color = art_dark, fontface = "bold",
    hjust = 0, vjust = 0.5, inherit.aes = FALSE
  ) +
  geom_text(
    data = channel_medians,
    aes(x = channel, y = 3e4,
        label = paste0("n = ", n_videos)),
    size = 2.5, color = art_mid, inherit.aes = FALSE
  ) +
  scale_fill_manual(values = channel_colors, guide = "none") +
  scale_color_manual(values = channel_colors, guide = "none") +
  scale_y_log10(
    labels = label_number(scale = 1e-6, suffix = "M"),
    breaks = c(1e4, 1e5, 1e6, 1e7, 1e8),
    minor_breaks = NULL
  ) +
  scale_x_discrete(labels = c(
    "Ethan Klein"     = "Ethan Klein",
    "H3 Podcast"      = "H3 Podcast",
    "Hila Klein"      = "Hila Klein",
    "h3h3Productions" = "h3h3Productions"
  )) +
  coord_flip() +
  labs(
    title    = "THE ORIGINAL CHANNEL STILL HITS HARDEST — <span style='color:#C0392B'>**4.5× THE MEDIAN**</span>",
    subtitle = "Per-Video View Count Distribution by Channel | Log Scale | 2013–2026",
    x        = NULL,
    y        = "Views Per Video (Log Scale)",
    caption  = "Data: YouTube Data API v3 | Artometrics Original Dataset\n— ARTOMETRICS"
  ) +
  theme_artometrics() +
  theme(panel.grid.major.y = element_blank())

p2

ggsave("chart2_channel_portfolio.png", plot = p2,
       path = ".", width = 12, height = 7, dpi = 300, bg = "white")
```

### [PLACEHOLDER — analysis coming]

---

## CHART 3 — THE OUTPUT MACHINE

### Episode Volume by Month, 2017–2026

```{r chart3-episode-volume}
#| echo: false
#| warning: false
#| message: false
#| fig-width: 10
#| fig-height: 6.5

era_levels_ep <- c(
  "Podcast Launch (2017–Sep 2020)",
  "Frenemies Era (Sep 2020–Jun 2021)",
  "Leftovers Era (Jun 2021–Oct 2023)",
  "Post-Leftovers (Oct 2023–2026)"
)

era_colors_ep <- c(
  "Podcast Launch (2017–Sep 2020)"    = art_secondary,
  "Frenemies Era (Sep 2020–Jun 2021)" = art_highlight,
  "Leftovers Era (Jun 2021–Oct 2023)" = art_purple,
  "Post-Leftovers (Oct 2023–2026)"    = art_teal
)

p3_data <- episodes |>
  mutate(
    airDate = as.Date(airDate),
    month   = floor_date(airDate, "month"),
    era     = case_when(
      airDate < as.Date("2020-09-15")                                    ~
        "Podcast Launch (2017–Sep 2020)",
      airDate >= as.Date("2020-09-15") & airDate < as.Date("2021-06-08") ~
        "Frenemies Era (Sep 2020–Jun 2021)",
      airDate >= as.Date("2021-06-08") & airDate < as.Date("2023-10-07") ~
        "Leftovers Era (Jun 2021–Oct 2023)",
      TRUE ~
        "Post-Leftovers (Oct 2023–2026)"
    ),
    era = factor(era, levels = era_levels_ep)
  ) |>
  count(month, era)

p3 <- ggplot(p3_data, aes(x = month, y = n, fill = era)) +
  geom_col(width = 28) +
  scale_fill_manual(
    values = era_colors_ep,
    guide  = guide_legend(nrow = 2, override.aes = list(size = 1))
  ) +
  scale_x_date(
    date_breaks = "1 year",
    date_labels = "%Y",
    expand      = c(0.01, 0)
  ) +
  scale_y_continuous(
    breaks = seq(0, 20, by = 2),
    expand = c(0, 0.3)
  ) +
  labs(
    title    = "THE <span style='color:#C0392B'>**2024 CLIFF**</span> — 72% DROP IN A SINGLE YEAR",
    subtitle = "Monthly Episode Count, H3 Podcast (Podchaser) | Colored by Era | 680 Episodes Total",
    x        = NULL,
    y        = "Episodes Released",
    fill     = NULL,
    caption  = "Data: Podchaser API, pulled April 2026 | Artometrics Original Dataset\n— ARTOMETRICS"
  ) +
  theme_artometrics() +
  theme(
    legend.position    = "bottom",
    legend.key.size    = unit(0.8, "lines"),
    legend.spacing.x   = unit(0.4, "cm"),
    panel.grid.major.x = element_blank()
  )

p3

ggsave("chart3_episode_volume.png", plot = p3,
       path = ".", width = 12, height = 7, dpi = 300, bg = "white")
```

### [PLACEHOLDER — analysis coming]

---

## CHART 4 — THE SEARCH STORY

### Google Trends: Four Keywords, One Brand Arc

```{r chart4-search-story}
#| echo: false
#| warning: false
#| message: false
#| fig-width: 10
#| fig-height: 6.5

trend_palette <- c(
  "h3h3"        = art_secondary,
  "ethan klein" = art_highlight,
  "frenemies"   = art_purple,
  "teddy fresh" = art_teal
)

# Strip pre-show frenemies signal — the word predates H3's use of it.
trends_chart4 <- trends |>
  filter(!(keyword == "frenemies" & date < as.Date("2020-09-01")))

trend_endpoints <- trends_chart4 |>
  group_by(keyword) |>
  filter(date == max(date)) |>
  ungroup()

key_events <- data.frame(
  date  = as.Date(c("2017-08-01", "2021-06-01")),
  hits  = c(100, 88),
  label = c("Fair Use\nLawsuit Win", "Frenemies\nFinale"),
  color = c(art_secondary, art_highlight),
  vjust = c(-0.7, -0.7),
  hjust = c(0.5, 0.5)
)

p4 <- trends_chart4 |>
  ggplot(aes(x = date, y = hits, color = keyword, group = keyword)) +
  geom_line(linewidth = 0.75, alpha = 0.9) +
  geom_point(
    data        = key_events,
    aes(x = date, y = hits),
    color       = key_events$color,
    inherit.aes = FALSE,
    size        = 3
  ) +
  geom_text(
    data        = key_events,
    aes(x = date, y = hits, label = label),
    color       = key_events$color,
    inherit.aes = FALSE,
    size        = 2.6, fontface = "bold",
    vjust       = key_events$vjust,
    hjust       = key_events$hjust
  ) +
  scale_color_manual(
    values = trend_palette,
    guide  = guide_legend(nrow = 1, override.aes = list(linewidth = 2))
  ) +
  scale_x_date(
    date_breaks = "2 years",
    date_labels = "%Y",
    expand      = expansion(mult = c(0.01, 0.04))
  ) +
  scale_y_continuous(
    breaks = c(0, 25, 50, 75, 100),
    labels = c("0", "25", "50", "75", "100 (peak)"),
    limits = c(0, 110)
  ) +
  labs(
    title    = "SEARCH TELLS THE STORY OF <span style='color:#C0392B'>**THREE DIFFERENT H3S**</span>",
    subtitle = "Google Trends Monthly Search Interest (US), 2012–2026 | 100 = Peak | Frenemies shown from Sep 2020 premiere",
    x        = NULL,
    y        = "Relative Search Interest",
    caption  = "Data: Google Trends via gtrendsR v1.5.2 | Monthly granularity | All values relative — not comparable across keywords\n— ARTOMETRICS"
  ) +
  theme_artometrics() +
  theme(
    legend.position   = "bottom",
    legend.title      = element_blank(),
    legend.text       = element_text(size = 9, color = art_dark),
    legend.key        = element_rect(fill = art_cream, color = NA),
    legend.key.width  = unit(1.8, "cm"),
    legend.spacing.x  = unit(0.4, "cm")
  )

p4

ggsave("chart4_search_story.png", plot = p4,
       path = ".", width = 12, height = 7, dpi = 300, bg = "white")
```

### [PLACEHOLDER — analysis coming]

---

## CHART 5 — THE CULTURAL FOOTPRINT

### Wikipedia Monthly Pageviews, All Four H3 Articles

```{r chart5-wikipedia}
#| echo: false
#| warning: false
#| message: false
#| fig-width: 10
#| fig-height: 6.5

wiki_palette <- c(
  "H3 Podcast"        = art_secondary,
  "h3h3Productions"   = art_highlight,
  "Teddy Fresh"       = art_teal,
  "Leftovers Podcast" = art_purple
)

p5 <- wiki |>
  ggplot(aes(x = date, y = pageviews, color = article, group = article)) +
  geom_line(linewidth = 0.75, alpha = 0.9) +
  geom_vline(
    xintercept = as.Date("2025-05-01"),
    linetype   = "dashed",
    color      = art_highlight,
    linewidth  = 0.55
  ) +
  annotate(
    "text",
    x     = as.Date("2025-05-01"),
    y     = Inf,
    label = "May 2025\nSynchronized Spike",
    vjust = 1.3, hjust = -0.07,
    size  = 2.7, color = art_highlight, fontface = "bold"
  ) +
  scale_color_manual(
    values = wiki_palette,
    guide  = guide_legend(nrow = 1, override.aes = list(linewidth = 2))
  ) +
  scale_x_date(
    date_breaks = "1 year",
    date_labels = "%Y",
    expand      = expansion(mult = c(0.01, 0.04))
  ) +
  scale_y_continuous(labels = label_comma()) +
  labs(
    title    = "THE WIKIPEDIA PAGES ARE A <span style='color:#C0392B'>**CULTURAL SEISMOGRAPH**</span>",
    subtitle = "Monthly Wikipedia Pageviews by Article | 2016–2026",
    x        = NULL,
    y        = "Pageviews",
    caption  = "Data: Wikimedia REST API, pulled April 2026 | Coverage varies — pages created at different dates\n— ARTOMETRICS"
  ) +
  theme_artometrics() +
  theme(
    legend.position   = "bottom",
    legend.title      = element_blank(),
    legend.text       = element_text(size = 9, color = art_dark),
    legend.key        = element_rect(fill = art_cream, color = NA),
    legend.key.width  = unit(1.8, "cm"),
    legend.spacing.x  = unit(0.4, "cm")
  )

p5

ggsave("chart5_wikipedia.png", plot = p5,
       path = ".", width = 12, height = 7, dpi = 300, bg = "white")
```

### [PLACEHOLDER — analysis coming]

---

## LIMITATIONS

### [PLACEHOLDER — limitations coming]

---

## CONCLUSION

### [PLACEHOLDER — conclusion coming]

*— KSM*

---

## REFERENCES

- YouTube Data API v3. Google.
  https://developers.google.com/youtube/v3

- Artometrics Original Dataset (April 2026). *H3 Podcast YouTube
  Network, 2013–2026*. Compiled via YouTube Data API v3.
  https://github.com/Artometrics/h3

- Wikimedia Foundation. (2026). *Wikipedia pageview statistics*.
  Retrieved via Wikimedia REST API.
  https://wikimedia.org/api/rest_v1/

- Google Trends. (2026). *Search interest data: h3h3, ethan klein,
  frenemies, teddy fresh*. Retrieved via gtrendsR v1.5.2.
  https://trends.google.com

- Podchaser. (2026). *H3 Podcast episode data, 2017–2026*.
  Retrieved via Podchaser API v1.
  https://api.podchaser.com

---

## EDITOR'S NOTE

This report was researched, written, designed, and produced in active
collaboration with Claude AI (Anthropic). The data pipeline, statistical
analysis, chart design, written analysis, narrative structure, and
visual styling were all developed through a directed partnership between
human editorial judgment and AI execution.

Artometrics was built on the premise that rigorous analysis and honest
process are not in conflict. The research questions, editorial instincts,
interpretive framing, and brand vision are ours. The execution — every
line of R code, every paragraph of analysis, every design decision —
was a collaboration. We document this not as a disclaimer but as a
description of how we actually work, and as a position: we believe this
is what serious data journalism looks like when the tools available are
used honestly and at full capacity.

*— Artometrics Editorial*